\LARGE \bf Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty [v-14 09-30-2014]

### 2014-10-02 paper.tex
fixed many little bugs

\vspace{-2ex}
\begin{equation}
p(\textbf{n}_i ) = \int_a^b   p\big(\textbf{n}_i = \textbf{v} | \textbf{c}_i = \gamma(t) \big)p\big(\textbf{c}_i = \gamma(t)\big) dt
\end{equation}

Grasp metrics such as  Ferrari-Canny require $\textbf{n}_i$ be normalized, or, equivalently, a member of the sphere $\mathcal{S}^{d-1}$ \cite{ferrari1992}. To account for this we densely sample from the  distribution $p \big(\textbf{n}_i ) \big)$  and project onto $\mathcal{S}^{d-1}$.  In Fig.\ref{fig:GraspDIst}, we visualize the theoretical distribution on $\textbf{n}_i$ calculated for a given GPIS and approach line of action.

@@

After formally deriving each distribution,  we can now sample along each line of action $\gamma_i(t)$ from the joint distribution $p(\textbf{c}_i,\textbf{n}_i | \gamma_i(t))$, due to our independence assumption Eq. \ref{eq:independence}. This can be done by drawing samples from Eq. \ref{eq:joint_contact_normal}. and using our projection technique for the normal distribution.

@@

\section{Experiments}
For the experiments below we used common household objects shown in Fig. \ref{fig:GPIS_TSDF}. We manually created a 25 x 25 grid, by tracing a pointcloud of the object on a table taken with a Primesense Carmine depth sensor. To accompany the SDF, we created an occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values. The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes. Our visualization technique follows the approach of \cite{jeffs} and consisted of drawing many shape samples from the distribution and blurring accordingly to a histogram equalization scheme.

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width = 17cm, height = 12cm]{figures/Slide09.jpg}
\caption{ \footnotesize Top: Comparison of two sampling methods. Red is the multi-arm bandit method that actively chooses which one to sample and Blue is the naive Monte-Carlo method. We measure their ability to converge in terms of simple regret averaged over 100 runs. We had them determine the best grasp when $|G|=1000$. In all cases the bandit method converges a least a magnitude faster than the pure Monte-Carlo integration. Bottom: Three objects from our data set that we tested on (Tape, Loofa, Water Bottle), we used a visualization technique described in \cite{jeffs}}
\vspace*{-10pt}
\label{fig:simple_regret}
\end{figure*}

@@

Sampling from our distribution $p(g)$ over $p(S)$ yields a reduction in computationally complexity, but only if the number of grasps one wants to evaluate remains small relative to $n^3$, techniques to ensure this could be to find locally optimal potential grasps using optimization approaches \cite{jeffs}.

>>>>

\vspace{-2ex}
\begin{equation}
    p(\textbf{n}_i ) = \int_a^b   p\big(\textbf{n}_i = \textbf{v} | \textbf{c}_i = \gamma(t) \big)p\big(\textbf{c}_i = \gamma(t)\big) dt \label{eq:normal_dist}
\end{equation}

Grasp metrics such as  Ferrari-Canny require $\textbf{n}_i$ be normalized, or, equivalently, a member of the sphere $\mathcal{S}^{d-1}$ \cite{ferrari1992}. To account for this we densely sample from the  distribution $p \big(\textbf{n}_i ) \big)$  and project onto $\mathcal{S}^{d-1}$.  In Fig.\ref{fig:GraspDist}, we visualize the distribution on $\textbf{n}_i$ calculated for a given GPIS and approach line of action.

@@

After formally deriving each distribution,  we can now sample along each line of action $\gamma_i(t)$ from the joint distribution $p(\textbf{c}_i,\textbf{n}_i | \gamma_i(t))$, due to our independence assumption Eq. \ref{eq:independence}. This can be done by drawing samples from the GP for signed distance and normals simultaneously and using our projection technique for the normal distribution.

@@

\section{Experiments}
For the experiments below we used common household objects.  The objects used can be found at \url{http://rll.berkeley.edu/grasping/} We manually created a 25 x 25 grid, by tracing a pointcloud of the object on a table taken with a Primesense Carmine depth sensor. To accompany the SDF, we created an occupancy map, which holds 1 if the point cloud was observed and 0 if it was not observed, and a measurement noise map, which holds the variance 0-mean noise added to the SDF values. The parameters of the GPIS were selected using maximum likelihood on a held-out set of validation shapes. Our visualization technique follows the approach of \cite{mahler2015opt} and consisted of drawing many shape samples from the distribution and blurring accordingly to a histogram equalization scheme.

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width = 17cm, height = 12cm]{figures/Slide09.jpg}
\caption{ \footnotesize Top: Comparison of two sampling methods. Red is the multi-arm bandit method that actively chooses which one to sample and Blue is the naive Monte-Carlo method. We measure their ability to converge in terms of simple regret averaged over 100 runs. We had them determine the best grasp when $|G|=1000$. In all cases the bandit method converges a least a magnitude faster than the pure Monte-Carlo integration. Bottom: Three objects from our data set that we tested on (Tape, Loofa, Water Bottle), we used a visualization technique described in \cite{mahler2015opt}}
\vspace*{-10pt}
\label{fig:simple_regret}
\end{figure*}

@@

Sampling from our distribution $p(g)$ over $p(S)$ yields a reduction in computationally complexity, but only if the number of grasps one wants to evaluate remains small relative to $n^3$, techniques to ensure this could be to find locally optimal potential grasps using optimization approaches \cite{mahler2015opt}.
